Rjags parameters

### 2020-09-12 Scripts/Rjags.tunning.Rmd
models by site

We can modify the initial parameters by hard-coding a maximum value for the false positive rate; or by picking it up from a left-skewed beta distribution
```{r}
library(tidyverse)
library(vegan)
library(rjags)
library(proxy)
library(here)

@@

## Custom functions
```{r}
model.round.nested <- function(list.hashes,n){
  require(dplyr)
  tibble.out <- paste("model", n , sep=".")
  tibble.in <- "data"
  tibble.in <- rlang::ensym(tibble.in)
  list.hashes <- mutate (list.hashes, !!tibble.out := map (!!tibble.in,  ~jags_for_presence(.x)))
}
sink("RoyleLink_prior.txt")
										cat("model {
										    # Priors
										     psi ~ dunif(0,1)
										    p11 ~ dunif(0.01,1)
										    p10 ~ dbeta(1,50)

@@

# Subset 
 ASV.nested %>% 
   ungroup() %>% 
   select(Step2.tibble) %>% 
  unnest(Step2.tibble) %>% 
  ungroup() %>% 
  separate(sample, into = c("biol","rep"), sep = "\\.") %>%
  separate(biol, into = c("Site", "biol")) %>% 
  group_by(Site) %>% 
  nest() %>% 
  mutate(data = map(data,
                    function(.y){
                      .y %>% 
                        mutate (nReads = 1) %>% 
                        spread(key = "rep", value = "nReads", fill= 0,drop = F)
  })) %>% 
  unnest() %>% 
  unite(Site, Hash, col = "key", sep = ".", remove = F) %>% 
# Select one  
  filter(key %in% unique.by.site$key) %>% 
  select(-key) %>% group_by(Site, Hash) %>% 
  nest %>% 
  group_by(Site) %>% 
  nest -> like.this 
```
Finally - run it ten times
```{r}
like.this %>% 
  mutate(Hashes = map (data , ~select(.x, Hash))) -> like.this
# Run 10 times
for (i in 1:10){
  like.this <- model.round.nested(like.this, n = i)
}
like.this %>% mutate(model.10chain = map(data, jags_for_presence)) -> all.combos.10chain
```

>>>>

We can modify the initial parameters by hard-coding a maximum value for the false positive rate; or by picking it up from a left-skewed beta distribution
```{r}
library(tidyverse)
library(vegan)
library(rjags)
library(proxy)
library(here)
library(unmarked)
library(jagsUI)

@@

## Custom functions
```{r}
model.round.nested <- function(list.hashes,n){
  require(dplyr)
  tibble.out <- paste("model", n , sep=".")
  tibble.in <- "data"
  tibble.in <- rlang::ensym(tibble.in)
  list.hashes <- mutate (list.hashes, !!tibble.out := map (!!tibble.in,  ~jags_for_presence(.x)))
}

ProbOcc <- function(x, psi, p11, p10, K){
 (psi*(p11^x)*(1-p11)^(K-x)) / ((psi*(p11^x)*(1-p11)^(K-x))+(((1-psi)*(p10^x))*((1-p10)^(K-x))))
}
sink("RoyleLink_prior.txt")
										cat("model {
										    # Priors
										     psi ~ dunif(0,1)
										    p11 ~ dunif(0.01,1)
										    p10 ~ dbeta(1,50)

@@

# Subset 
 ASV.nested %>% 
   ungroup() %>% 
   select(Step2.tibble) %>% 
  unnest(Step2.tibble) %>% 
  ungroup() %>% 
  separate(sample, into = c("biol","rep"), sep = "\\.") %>%
  separate(biol, into = c("Site", "biol")) %>% 
  group_by(Site) %>% 
  nest() %>% 
  mutate(data = map(data,
                    function(.y){
                      .y %>% 
                        mutate (nReads = 1) %>% 
                        spread(key = "rep", value = "nReads", fill= 0,drop = F)
  })) %>% 
  unnest() %>% 
  unite(Site, Hash, col = "key", sep = ".", remove = F) %>% 
# Select one  
  filter(key %in% unique.by.site$key) %>% 
  select(-key) %>% group_by(Site, Hash) %>% 
  nest %>% 
  group_by(Site) %>% 
  nest -> like.this 
```
Finally - run it ten times
```{r}
like.this %>% 
  mutate(Hashes = map (data , ~select(.x, Hash))) -> like.this
# Run 10 times
for (i in 1:10){
  like.this <- model.round.nested(like.this, n = i)
}
like.this %>% mutate(model.10chain = map(data, jags_for_presence)) -> all.combos.10chain

all.combos.10chain %>% write_rds(here("Input", "10chain.rds"))

all.combos.10chain %>% unnest(cols = c(Hashes, starts_with("model")), names_repair = "unique") -> row.df

row.df %>% ungroup() %>% rowwise(Site, Hash) %>% summarise(mean = mean(c_across(where(is.numeric))))
```
